---
title: "p8105_hw5_bs3142"
author: "Bingyu Sun"
date: "11/3/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
) 

library(tidyverse) #load library

theme_set(theme_bw() + theme(legend.position = "bottom")) #define graph format
```

## Problem 1

### Data import

```{r, data_exp_import}
read_study = function(flnm) {
  read_csv(flnm) %>%
    mutate(filename = flnm)
} #create function to read file and a new column for filenames

study_data = 
  list.files(path = "./data/data_exp",
             pattern = "*.csv",
             full.names = TRUE) %>% #get dataframe of filenames with relative file path
  map_df(~read_study(.x)) #read data from each file
```

### Data tidying

```{r, data_exp_tidy}
tidy_study =
  study_data %>%
  mutate(filename = str_replace_all(filename, c("^./data/data_exp/" = "", ".csv$" = ""))) %>% #clean up filename
  separate(filename, into = c("treatment", "id"), sep = "_") %>% #separate filename to two variables as treatment and id
  mutate(treatment = str_replace_all(treatment, c("con" = "control", "exp" = "experiment"))) %>% #rename con to control, exp to experiment
  gather(key = week, value = value, week_1:week_8) %>% #change to long format
  mutate(week = str_replace(week, "^week_", "")) #clean names of week variable
```

### Spaghetti plot

```{r, dpi = 300, data_exp_spaghetti}
tidy_study %>%
  mutate(week = as.numeric(week)) %>%
  group_by(treatment, id) %>% 
  ggplot(aes(x = week, y = value, color = id)) +
  geom_line() +
  facet_grid(~treatment) + #create 2-panel plot by treatment
  labs(
    title = "Observations of Each Subject Over Time by Treatment"
  ) +
  viridis::scale_color_viridis(
    name = "Subject ID",
    discrete = TRUE
  ) +
  scale_x_continuous(breaks = c(1:8)) #plot spagetti plot
```

Comment:

In general, there is an increase in performance over time in the experimental group comparing to the control group, suggesting a positive correlation between treatment and participants' performance in the experiment arm. For controls, the participants' performances fluctuate around baseline, revealing the change in the experimental arm is probably due to treatment.

## Problem 2

### Data import

```{r, cases_data_import}
cases_raw = read_csv("./data/homicide-data.csv") #import data

str(cases_raw)
names(cases_raw)
```

**Description**

The dataset consists of homicide information in 50 large U.S. cities, each row is a case showing victim information (name, race, age, sex), murder date, location information (city, state, latitude, longitude), and disposition information of the case. There are a total of **`r nrow(cases_raw)`** cases.

### Data manipulation

```{r, cases_data_cleaning}
cases_tidy =
  cases_raw %>%
  mutate(city_state = str_c(city, ",", state)) %>% #get a new variable city_state
  mutate(disposition = str_replace_all(disposition, c("Closed without arrest" = "Unsolved", "Open/No arrest" = "Unsolved"))) #combine two categories to one category called unsolved
```

#### Q & A

**1. Summarize within cities to obtain the total number of homicides, and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).**

```{r, q2_sec1}
cases_nest =
  cases_tidy %>%
  group_by(city_state) %>%
  nest() %>% #get dataframes by city
  mutate(
    n_total = map(.x = data, ~ .x %>% 
                    pull(disposition) %>%
                    length()),
    n_unsolved = map(.x = data, ~ .x %>%
                       filter(disposition == "Unsolved") %>%
                       pull(disposition) %>%
                       length())
  ) %>% #get number of homicides and unsolved homicides
  select(-data)

cases_nest %>%
  knitr::kable(digits = 0) #show numbers in a table
```

**2. For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.**

```{r, q2_sec2}
bal_result = prop.test(cases_nest$n_unsolved[[3]], cases_nest$n_total[[3]]) #prop.test for Baltimore

tibble(
  estimate = broom::tidy(bal_result) %>% pull(estimate),
  conf.low = broom::tidy(bal_result) %>% pull(conf.low),
  conf.high = broom::tidy(bal_result) %>% pull(conf.high)
) #show results in a dataframe
```

**3. Run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.**

```{r, q2_sec3}
prop_test = function(x, n) {
  
  prop_result = prop.test(x, n)
  
  tibble(estimate = broom::tidy(prop_result) %>% pull(estimate),
         conf.low = broom::tidy(prop_result) %>% pull(conf.low),
         conf.high = broom::tidy(prop_result) %>% pull(conf.high)
         )
  
} #create a function to show statistics of interest in a dataframe

prop_test_results = 
  cases_nest %>%
  mutate(statistics = map2(.x = cases_nest$n_unsolved, .y = cases_nest$n_total, 
                           ~ prop_test(x = .x, n = .y))) %>% #a new variable for test statistics applies to each sub-dataframes
  select(city_state, statistics) %>%
  unnest() #convert back to one dataframe

prop_test_results %>%
  knitr::kable(digits = 3) #show result in a table
```

**4. Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.**

```{r, dpi = 300, q2_sec4_plot}
prop_test_results %>%
  mutate(city_state = forcats::fct_reorder(city_state, estimate)) %>% #reorder x-axis variable based on estimate
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + #add errorbar
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Estimate of the Proportion of Unsolved Homicides in each City"
  ) #plot scatterplot
```

